Was Devon Allen Unjustly Disqualified at the 2022 World Track and Field Championships?

### 2023-04-04 Manuscript/manuscript.tex
fixed two left quotes

2)
Outside the blog posts from LetsRun.com, there have not been any published
papers regarding Devon Allen's disqualification in particular.  This is not
particularly surprising given that his disqualification occurred only last August.
Letsrun is a website that is part message board and part news.  The message board,
which functions similarly to Reddit is very active during important running
events, which include during the finals of major events such as
the Olympics and the World Track and Field Championships.  However, it is the
news section of the website that generated articles such as "Was Devon Allen
Screwed? There's At Least a 99\% That He Was" and "The Data Keeps Pouring In and
It Continues to Look Bad For World Athletics and Great For Devon Allen".  Robert
Johnson, who created and runs the Letsrun website argued that there was an error
with the timing equipment at the 2022 Track and Field World Championship and
cited graphs, statistics such as median reaction time, and compared the reaction
times at the 2022 Track and Field World Championship.

>>>>

2)
Outside the blog posts from LetsRun.com, there have not been any published
papers regarding Devon Allen's disqualification in particular.  This is not
particularly surprising given that his disqualification occurred only last August.
Letsrun is a website that is part message board and part news.  The message board,
which functions similarly to Reddit is very active during important running
events, which include during the finals of major events such as
the Olympics and the World Track and Field Championships.  However, it is the
news section of the website that generated articles such as ``Was Devon Allen
Screwed? There's At Least a 99\% That He Was" and ``The Data Keeps Pouring In and
It Continues to Look Bad For World Athletics and Great For Devon Allen".  Robert
Johnson, who created and runs the Letsrun website argued that there was an error
with the timing equipment at the 2022 Track and Field World Championship and
cited graphs, statistics such as median reaction time, and compared the reaction
times at the 2022 Track and Field World Championship.
